APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
add example from StackOverflow

Direct use of this idiom would not have any benefit
over using the individual stages of the sub-pipeline directly,
as both approaches would simply produce a linear pipeline.
However, the recursion support shines in more complex situations
that involve the construction of estimators using \textit{meta-estimators}.
These are objects in the scikit-learn API
that wrap an estimator to give it additional functionality.
An example of meta-estimators are object of the class
\texttt{OneVsRestClassifier},
which can be used to construct a multi-label classifier
\citep{tsoumakas2007multi}
from an ordinary binary classifier object
by constructing one binary classifier per class
(a strategy variously called one-vs.-the-rest,
one-vs.-all or binary relevance).

% TODO insert example from http://stackoverflow.com/q/16437022/166749 here

>>>>

Direct use of this idiom would not have any benefit
over using the individual stages of the sub-pipeline directly,
as both approaches would simply produce a linear pipeline.
However, the recursion support shines in more complex situations
that involve the construction of estimators using \textit{meta-estimators}.
These are objects in the scikit-learn API
that wrap an estimator to give it additional functionality.
An example of meta-estimators are object of the class
\texttt{OneVsRestClassifier},
which can be used to construct a multi-label classifier
\citep{tsoumakas2007multi}
from an ordinary binary classifier object
by constructing one binary classifier per class
(a strategy variously called one-vs.-the-rest,
one-vs.-all or binary relevance):

\begin{verbatim}
ovr_svm = OneVsRestClassifier(LinearSVC())
\end{verbatim}

The \texttt{ovr\_svm} object can be passed to a hyperparameter search
producedure directly to determine parameters such as $C$,
but the syntax to do that has changed.
The object under consideration is no longer a \texttt{LinearSVC}
but a \texttt{OneVsRestClassifier},
which exposes the former object as its public attribute \texttt{estimator}.
Double underscore syntax must be used to address $C$,
i.e.\ \texttt{estimator\_\_C}.

To make this example more interesting,
feature selection using $\chi^2$ tests can be added to the SVM,
such that each of the separate binary classification problems
gets its own set of features.
This can be done by wrapping a pipeline in an OvR object:

\begin{verbatim}
svm_chi2 = Pipeline(["chi2", SelectKBest(chi2)],
                    ["svm", LinearSVC()])
ovr_svm = OneVsRestClassifier(svm_chi2)
\end{verbatim}

Now, the parameter $k$ specifying number of features to be kept
in each $\chi^2$ feature selection step
is exposed by \texttt{ovr\_svm} as \texttt{estimator\_\_chi2\_\_k},
mirroring the nesting of estimators in meta-estimators,
and can be optimized by grid search or random search.

Taking the example one step further to arrive at recursive pipelines,
the \texttt{ovr\_svm} object can be combined
with a \textsf{tf--idf} document vectorizer
to obtain a full document classification pipeline
that takes a stream of text files, paired with class labels, as input:

\begin{verbatim}
doc_clf = Pipeline(["tfidf", TfidfVectorizer()],
                   ["clf", ovr_svm])
\end{verbatim}

The double underscore syntax again serves to address attributes
in this triply nested structure,
so the linear SVM's $C$ parameter
is now called \texttt{clf\_\_estimator\_\_svm\_\_C}.

Following the Python mantra that ``explicit is better than implicit,''
the implementers of scikit-learn have resisted the temptation
to implement shortcuts in the notation,
for example to allow addressing of attributes
of the underlying estimator of the OvR classifier
without the intermediate \texttt{estimator}.
Doing so might require conflict resolution
when an attribute of the meta-estimator object itself
has the same name as an attribute on the wrapped estimator.
The rules for such conflict resolution would need to be
designed, implemented, tested, and, equally important, documented
such as to be understandable for users.
So, the cost of ``syntactic sugar'' was avoided
at the expense of some typing by the user and some loss of elegance.
